Stat 400 Project

### 2021-12-03 Stat 400 proj.Rmd
test
fix merge conflict

```{r}
library(tidyverse)

@@

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist){

@@

  #Check to see which suceptable subjects get infected
  #For loop
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }else{new_status[j] <- 'S'}
    }
  }

@@

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

@@

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change)
    checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    new_status <- infection_status(checked_positions, 2)
    checked_positions[,3] <- new_status
    end_day[[i]] <- checked_positions

    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[[i-1]], change)
    checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    new_status <- infection_status(checked_positions, 1/5)
    checked_positions[,3] <- new_status
    end_day[[i]] <- checked_positions

@@

#S,I,R data
suceptable = function(){

recovered = function(){

infected = function(){

#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
```

This method is takes another approach. It's somewhat similar to the step function, but this one randomly changes the location of the individuals on a daily basis. Then at that point we gather its neighbors and calculate probability of them becoming infected. We keep track of those who have come in contact and

``` {r}
#for knn
#install.packages('dbscan') 
library("dbscan")
```

``` {r}
#variables
incubation_time <- rgamma(5, 6, (2/3))
crucial_distance <- rexp(5, 1/8)
n = 2000
starting_infected_prob = 0.005

#starting data and plot
starting_values = data.frame(cbind(1:n),
                             cbind(runif(n,0,1),
                             runif(n,0,1),
                             rbinom(n,1,starting_infected_prob)),
                             cbind(rep(0,n)))

colnames(starting_values) = c("id","x","y","infected","susceptible")

#this plot represents the random distribution of 2000 people in a 1km^2 area, with the blue dots being the infected individuals. Instead of trying to track progression of time, as the paper illustrates, my thought was to randomize the dot locations each iteration. Each iteration represents a day. The infected individual will be in another random location each day. 
ggplot() + geom_point(aes(starting_values[,2],starting_values[,3],colour = starting_values[,4])) + xlab("x coordinate") + ylab("y coordinate")
```

```{r}

#this calculates the distance from an infected individual
point_dist = function(x1,y1,x2,y2){
  val = sqrt((x2-x1)^2+(y2-y1)^2)
  return(val)
}

#calculates the probability of infection
#d = current distance from infected, dr = critical value to achieve certain probability of infection
probability_of_infection = function(d,dr){
  sigmoid = 1/(1+d*exp(d-dr))
  return(sigmoid)
}

#returns data frame of current infected infected individuals
infected_idx = function(df){
  idx = df[df$infected==1,]
  return(idx)
}

#this function returns a data frame of indexes of people considered susceptible. This function aims to calculate the distances of k neighbors then returns a df of indecies of those in neighborhood. We will need to keep a running track of the id's of susceptible neighbors and later factor in the probability of becoming infected.
sus = function(df,idx){

  dist_arr = point_dist(df[,2],df[,3],df[idx,2],df[idx,3])
  nn = kNN(dist_arr,k = 9)
  nnidx = nn$id[idx,]
  return(nnidx)
}

#estimate the probability one recovers
recovered = function(df){
  #lower probability of contracting again
}

@@

``` {r}
simulator = function(start,b){
  current_infected = infected_idx(start)

}
```

>>>>

```{r}
#testing github
library(tidyverse)

@@

#Function for deciding if infections occured
#BUG -- If the mean_crit_dist is small, all infections go away!!
#BUG -- Sometimes d is NA, I assume it's when indv goes off map. 
infection_status <- function(state, mean_crit_dist,day_r,rt){

@@

  #Check to see which susceptible subjects get infected
  #For loop

  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)

      if(d <= crucial_distance){
        new_status[j] <- 'I'

        newly_infected <- c(newly_infected, j)
      }else{new_status[j] <- 'S'}

      #if day is past recovery time, set to recovered
      else if(day_r >= rt){
        new_status[j] <- 'R'
      }

      else{
        new_status[j] <- 'S'
      }
>>>>>>> infection status update
    }
  }

@@

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)

@@

  recovery_time <- c()

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)

    updated_positions <- update_coords(initial_data, change)
    checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    new_status <- infection_status(checked_positions, 2)
    checked_positions[,3] <- new_status
    end_day[[i]] <- checked_positions

    updated_positions <- update_coords(initial_data, change)#, x_dim, y_dim)x_dim,y_dim not parameters
    # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2,i,14)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)

    updated_positions <- update_coords(end_day[[i-1]], change)
    checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    new_status <- infection_status(checked_positions, 1/5)
    checked_positions[,3] <- new_status
    end_day[[i]] <- checked_positions

    updated_positions <- update_coords(end_day[[i-1]], change)#, x_dim, y_dim) #x_dim,y_dim not parameters in update_coords
    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)

    rand_recovery_time <- rpois(1,14)
    new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)

    end_day[[i]] <- cbind(updated_positions, new_status)

@@

x = simulator(100,25,1,1,2)

@@

Plots
``` {r}
ggplot() + 
  geom_line(aes())
```

```{r}
#reported monte carlo summary data
qd = c(0,25,50,75)
pos = c(99.3,99.2,98.7,92.7)
dncpv = c(69,53,46,33)
dncpt = c(26,32,43,42)
r0 = c(1.8,1.73,1.8,1.63)
mcsum = cbind(qd,pos,dncpv,dncpt,r0)
colnames(mcsum,c("Quarantine degree [%]",	"Percentage of size %",	"DNC peak value [cases]",	"DNC peaking time [days]",	"R0"))
```
